Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-01-27 manuscript.tex
changing some figures
minimal changes

Intraplate seismicity is a hard problem to solve in tectonics, mainly during the lack of observed seismicity in many areas where seismic hazard assesment are also difficult and the methods applied are often close correlated to the geometries defined by the experts with valuable criteria.

Three smoothing seismicity techniques are reviewed and their application tothe Brazilian seismicity and a seismic hazard assesment are discussed.

@@

The method of \citet{frankel_1995} uses a \emph{fixed} bandwidth in space. \citet{woo_1996} suggests a bandwidth as function of the \emph{magnitude}. \citet{helmstetter_2012} propose a \emph{locally-adaptive} kernel bandwidths in space and time, chosen for each event.
This last one was proposed initialy to take care of the background seismicity rate in the context of long-term earthquake forecast and the time-independent assumption about the annual background seismic rate could be used
(not indiscriminately REFERENCE) as a grid of points seismic sources.

@@

The Brazilian seismic hazard building code (REFERENCE) [ABNT] was based on the GSHAP results for South America, which is the last published model for the whole region. Howerver, some significant seismic areas (Porto dos Gaúchos [REFERENCIA]), are not represented in the GPSHAP-based building codes.

@@

In the kernel density estimation both its shape and its bandwidth need to be defined. Most kernels are gaussian or power-laws in one of their variants. The main distinction between the methods described here is the bandwidth selection process.

\citet{frankel_1995} smoothing method applies a gaussian \citet{nadaraya_1964}-\citet{watson_1964} smoothing technique with a \emph{fixed} smoothing-distance bandwidth to estimate the seismicity rate. \citet{woo_1996} proposes a \emph{magnitude-dependent} kernel bandwidth based on the nearest neighbour mean distance in magnitude bins. \citet{helmstetter_2012} proposes a \emph{locally-adaptive} bandwidth, based on kernel estimations for the background seismicity rate in long-term forecasts on both space and time dimensions.

@@

To perform the hazard computation, the OpenQuake suite was chosen. The modelling tool was the HMTK also available by GEM scientifical board. The Frankel method was already implemented on the toolkit and the other two was implemented in the context of this paper and they are free available on a public repository.

@@

\subsection{Specifical Purpose}

@@

\subsection{Catalog check}

@@

\subsection{Declustering procedures}

@@

\subsection{Frequency-magnitude distribution}

@@

\subsection{Catalog completeness}

@@

%------------------------------------------------
%
% smooothing methods
%
%------------------------------------------------
\section{Smoothing methods}
Three smoothing methods are now briefly explained.

\subsection{Frankel: fixed bandwidth}

Arthur \citet{frankel_1995} smoothing seismicity proposal consisted originally in using a "correlation distance" $d_F$ as the \textit{fixed} kernel bandwidth and applying the Nadaraya-Watson \citep{nadaraya_1964, watson_1964} estimator to smooth a 2D seismicity histogram using a gaussian kernel:
\begin{equation}
	\ensuremath{
		\tilde{n}_j = \frac{ \sum_{i} n_i \,e^{ - \left(\frac{\gls{sym:dij}}{\gls{sym:dF}}\right)^2}}
						   { \sum_{i}     e^{ - \left(\frac{\gls{sym:dij}}{\gls{sym:dF}}\right)^2}},
	}
	\label{eq:ni}
\end{equation}
where $\tilde{n}_j$ is the smoothed seismicity (number of earthquakes with magnitude $m$ above the minimum magnitude \gls{sym:Md} in the catalog) on cell $j$. $n_i$ is the earthquake counting in each other cell $i$ and \gls{sym:dij} is \glsdesc{sym:dij}.

\subsection{Woo: magnitude-dependent bandwidth}

\citet{woo_1996} suggested to evaluate the contribution of each earthquake $i$, located at $\boldsymbol{r}_i$, to the seismicity rate $R$ (number of earthquakes per year and unity area) on the cell centered in $\boldsymbol{r}$, depending on the magnitude $m$:
\begin{equation}
	\ensuremath{
		\gls{sym:Rrm} = \sum_{i=1}^{N} \frac{ K(\gls{sym:r} - \gls{sym:ri}, m)}
											{T({\gls{sym:ri})}},
	}
	\label{eq:Rrm}
\end{equation}
where $N$ is the number of earthquakes $i$ in the magnitude bin $m \pm \mathrm{d}m$,
and $T(\gls{sym:ri})$ is the completess time of magnitude $m$ observed on \gls{sym:ri}.

@@

Just to compare, in figure \ref{fig_woo_bandwidth} it is shown the functions computed by \citet{beauval_2003} for Norway and Spain. The angular coeficient ($a_1$) is in the same range of the others but the general mean distance between events into the same magnitude bin is higher than other countries. It is in some way expected. Brazil is quite large than mentioned countries.

\subsection{Helmstetter and Werner: locally-adaptive space and time bandwidths}

Even work on a forecast perspective, the background seismicity rate for a long-term time-independent forecast could be used to charachterize a diffused seismicity under the common assumption that this background seismic rate is invariant over time.

@@

\subsubsection{Local bandwidth computation}

@@

The bandwidths are defined locally. Could be small in high earthquake density regions and higher where earthquakes are rarelly or regions with information lack.

\subsubsection{Stationary seismic rate}
After compute the model parameters and completely define it, the time-independent or stationary seismic rate $\bar{R}$ on each location $\boldsymbol{r}_0$ have to be computed.
The way to do it proposed by \citet{helmstetter_2012} was to get the median
on $\boldsymbol{r}_0$ over all considered time window:
\begin{equation}
	\ensuremath{
		\bar{R}(\boldsymbol{r}_0) = \text{Median}\left[R(\boldsymbol{r}_0, t)\right].
	}
	\label{eq:stationary_rate}
\end{equation}

@@

\subsubsection{Maximum likelyhood optimization}

@@

If the earthquake occurrence could be modelled by a Poisson process with rate $N_p$, then the probability to observe exactly $n$ events on the consider time frame is
\begin{equation}
	\ensuremath{
		\gls{sym:pNn} = \frac{{N_p}^n e^{-N_p}}{n!}.
	}
	\label{eq:poisson_probability}
\end{equation}

@@

@@

\subsubsection{Simulation 2}

Suspendisse viverra eleifend nulla at facilisis. Nullam eget tellus orci. Cras sit amet lorem velit. Maecenas rhoncus pellentesque orci eget vulputate. Phasellus massa nisi, mattis nec elementum accumsan, blandit non neque. In ac enim elit, sit amet luctus ante. Cras feugiat commodo lectus, vitae convallis dui sagittis id. In in tellus lacus, sed lobortis eros. Phasellus sit amet eleifend velit. Duis ornare dapibus porttitor. Maecenas eros velit, dignissim at egestas in, tincidunt lacinia erat. Proin elementum mi vel lectus suscipit fringilla. Mauris justo est, ullamcorper in rutrum interdum, accumsan eget mi. Maecenas ut massa aliquet purus eleifend vehicula in a nisi. Fusce molestie cursus lacinia.

@@

@@

Nam fermentum sapien at enim varius consectetur. Quisque lobortis imperdiet mauris, et accumsan libero vulputate vitae. Integer lacinia purus vel metus tempus suscipit. Curabitur ac sapien quis mauris euismod commodo. Sed pharetra sem elit. Fusce ultrices, mauris eu fermentum tempor, tellus sem ornare lectus, in convallis nunc urna id dolor. Donec convallis ligula vitae sem viverra fermentum. Mauris in ullamcorper erat. Donec ultrices tempus nibh quis vestibulum.

Praesent volutpat, nibh in dignissim commodo, tellus justo consequat erat, vel consequat mi arcu vel lectus. Aliquam a tellus nec felis sagittis consequat. Quisque convallis imperdiet neque a tempor. Nulla non erat urna. Mauris vel lorem magna, tristique auctor ipsum. Aliquam pharetra eleifend massa. Donec porttitor sagittis luctus. Aliquam pretium luctus leo quis congue. Morbi vel felis mi. Suspendisse viverra tortor pretium orci lacinia eleifend. Phasellus aliquam, nunc eu cursus feugiat, erat odio porttitor libero, quis accumsan orci ipsum ut lorem. Vestibulum pharetra malesuada egestas. Sed non orci sit amet erat suscipit fringilla in et diam. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Nunc ut rhoncus nulla. Aenean porta rhoncus suscipit.

Suspendisse viverra eleifend nulla at facilisis. Nullam eget tellus orci. Cras sit amet lorem velit. Maecenas rhoncus pellentesque orci eget vulputate. Phasellus massa nisi, mattis nec elementum accumsan, blandit non neque. In ac enim elit, sit amet luctus ante. Cras feugiat commodo lectus, vitae convallis dui sagittis id. In in tellus lacus, sed lobortis eros. Phasellus sit amet eleifend velit. Duis ornare dapibus porttitor. Maecenas eros velit, dignissim at egestas in, tincidunt lacinia erat. Proin elementum mi vel lectus suscipit fringilla. Mauris justo est, ullamcorper in rutrum interdum, accumsan eget mi. Maecenas ut massa aliquet purus eleifend vehicula in a nisi. Fusce molestie cursus lacinia.

@@

\appendix

\section{Appendix Title}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.20\textwidth}
						 p{0.40\textwidth}
						 p{0.40\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_depth}  &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_weekday} &
		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_hour}
		\end{tabular}
	\end{table}
	\caption{Catalogue overview. The histogram (a) shows the depth distribution. The histograms (b) and (c) represent the distributions of weekday and hour which earthquakes occur respectly. Dashed lines represent the mean value.}
	\label{fig_overview}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_rate}
		\\
		\footnotesize(b)
		& \includegraphics[width=0.40\textwidth]{z_img_time_mag_count_br_1960}
		\end{tabular}
	\end{table}
	\caption{Earthquakes by year (a) and discriminated by magnitude (b).}
	\label{fig_records}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\begin{tabular}{ c c }
		\footnotesize(a)
		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_decluster}
		\\
		\footnotesize(b)
		& \includegraphics[width=0.40\textwidth]{z_img_hmtk_bsb2013_pp_decluster}
		\end{tabular}
	\end{table}
	\caption{Decluster evaluation (a) and the clusters map (b).}
	\label{fig_decluster}
	\end{center}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\linewidth]{z_img_hmtk_bsb2014_11_completeness}
	\caption{Annual earthquake recurrence.}
	\label{fig_occurrence}
\end{figure}

% =========
% Methods
% =========

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_woo_bandwidth}
	\caption{Magnitude dependence bandwidth.}
	\label{fig_woo_bandwidth}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_hidi}
	\caption{Local bandwidth example.}
	\label{fig_helmstetter_hidi}
\end{figure}

% TODO add HI_DI histograms

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_stationary_a}
	\caption{Stationary seismic rate}
	\label{fig_helmstetter_stationary_rate}
\end{figure}

\begin{figure}
	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
	\caption{Learning and target catalogs.}
	\label{fig_helmstetter_catalogues}
\end{figure}

% =========
% Smoothed Rates
% =========

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth}
						 p{0.34\textwidth}
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_a_frankel_br}  &
		\includegraphics[height=5cm]{z_img_a_woo} &
		\includegraphics[height=5cm]{z_img_a_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Smoothed rates comparission: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectly.}
	\label{fig_rates}
	\end{center}
\end{figure}

% =========
% Results
% =========

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.33\textwidth}
						 p{0.34\textwidth}
						 p{0.33\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c)
		\\
		\includegraphics[height=5cm]{z_img_pga_frankel}  &
		\includegraphics[height=5cm]{z_img_pga_woo} &
		\includegraphics[height=5cm]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{PGA (poe 10\%/50y) comparission for (a) \citet{frankel_1995}, (b) \citet{woo_1996} and (c) \citet{helmstetter_2012} methods.}
	\label{fig_pga}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
		\footnotesize(a)
		&
		\footnotesize(b)
		\\
		\includegraphics[width=0.45\textwidth]{z_img_pga_gshap} &
		\includegraphics[width=0.45\textwidth]{z_img_pga_helmstetter}
		\end{tabular}
	\end{table}
	\caption{Previous available Brazillian PSHA from (a) GSHAP project and the PSHA proposed by this work (b). }
	\label{placeholder}
	\end{center}
\end{figure}

>>>>

Intraplate seismicity is a hard problem to solve in tectonics, mainly during the lack of observed seismicity in many areas where seismic hazard assessment are also difficult and the methods applied are often close correlated to the geometries defined by the experts with valuable criteria.

Three smoothing seismicity techniques are reviewed and their application to the Brazilian seismicity and a seismic hazard assessment are discussed.

@@

The method of \citet{frankel_1995} uses a \emph{fixed} bandwidth in space. \citet{woo_1996} suggests a bandwidth as function of the \emph{magnitude}. \citet{helmstetter_2012} propose a \emph{locally-adaptive} kernel bandwidths in space and time, chosen for each event.
This last one was proposed initially to take care of the background seismicity rate in the context of long-term earthquake forecast and the time-independent assumption about the annual background seismic rate could be used
(not indiscriminately REFERENCE) as a grid of points seismic sources.

@@

The Brazilian seismic hazard building code (REFERENCE) [ABNT] was based on the GSHAP results for South America, which is the last published model for the whole region. However, some significant seismic areas (Porto dos Gaúchos [REFERENCIA]), are not represented in the GPSHAP-based building codes.

@@

In the kernel density estimation both its shape and its bandwidth need to be defined. Most kernels are Gaussian or power-laws in one of their variants. The main distinction between the methods described here is the bandwidth selection process.

\citet{frankel_1995} smoothing method applies a Gaussian \citet{nadaraya_1964}-\citet{watson_1964} smoothing technique with a \emph{fixed} smoothing-distance bandwidth to estimate the seismicity rate. \citet{woo_1996} proposes a \emph{magnitude-dependent} kernel bandwidth based on the nearest neighbor mean distance in magnitude bins. \citet{helmstetter_2012} proposes a \emph{locally-adaptive} bandwidth, based on kernel estimations for the background seismicity rate in long-term forecasts on both space and time dimensions.

@@

To perform the hazard computation, the OpenQuake suite was chosen. The modelling tool was the HMTK also available by GEM scientific board. The Frankel method was already implemented on the toolkit and the other two was implemented in the context of this paper and they are free available on a public repository.

@@

\subsection{Specific Purpose}

asdfasdfa

@@

%------------------------------------------------------------------------------
\subsection{Catalog check}
%------------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------
\subsection{Declustering procedures}
%------------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------
\subsection{Frequency-magnitude distribution}
%------------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------
\subsection{Catalog completeness}
%------------------------------------------------------------------------------

@@

%------------------------------------------------
% M E T O D O L O G Y 
%------------------------------------------------
\section{Smoothing methods}

Three smoothing methods are now briefly explained.

%------------------------------------------------------------------------------
\subsection{Frankel: fixed bandwidth}
%------------------------------------------------------------------------------

Arthur \citet{frankel_1995} smoothing seismicity proposal consisted originally in using a "correlation distance" $d_F$ as the \textit{fixed} kernel bandwidth and applying the Nadaraya-Watson \citep{nadaraya_1964, watson_1964} estimator to smooth a 2D seismicity histogram using a Gaussian kernel:
\begin{equation}
	\ensuremath{
		\tilde{n}_j = \frac{ \sum_{i} n_i \,e^{ - \left(\frac{\gls{sym:dij}}{\gls{sym:dF}}\right)^2}}
						   { \sum_{i}     e^{ - \left(\frac{\gls{sym:dij}}{\gls{sym:dF}}\right)^2}},
	}
	\label{eq:ni}
\end{equation}
where $\tilde{n}_j$ is the smoothed seismicity (number of earthquakes with magnitude $m$ above the minimum magnitude \gls{sym:Md} in the catalog) on cell $j$. $n_i$ is the earthquake counting in each other cell $i$ and \gls{sym:dij} is \glsdesc{sym:dij}.

%------------------------------------------------------------------------------
\subsection{Woo: magnitude-dependent bandwidth}
%------------------------------------------------------------------------------

\citet{woo_1996} suggested to evaluate the contribution of each earthquake $i$, located at $\boldsymbol{r}_i$, to the seismicity rate $R$ (number of earthquakes per year and unity area) on the cell centered in $\boldsymbol{r}$, depending on the magnitude $m$:
\begin{equation}
	\ensuremath{
		\gls{sym:Rrm} = \sum_{i=1}^{N} \frac{ K(\gls{sym:r} - \gls{sym:ri}, m)}
											{T({\gls{sym:ri})}},
	}
	\label{eq:Rrm}
\end{equation}
where $N$ is the number of earthquakes $i$ in the magnitude bin $m \pm \mathrm{d}m$,
and $T(\gls{sym:ri})$ is the completeness time of magnitude $m$ observed on \gls{sym:ri}.

@@

Just to compare, in figure \ref{fig_woo_bandwidth} it is shown the functions computed by \citet{beauval_2003} for Norway and Spain. The angular coefficient ($a_1$) is in the same range of the others but the general mean distance between events into the same magnitude bin is higher than other countries. It is in some way expected. Brazil is quite large than mentioned countries.

%------------------------------------------------------------------------------

\subsection{Helmstetter and Werner: locally-adaptive space and time bandwidths}
%------------------------------------------------------------------------------

Even work on a forecast perspective, the background seismicity rate for a long-term time-independent forecast could be used to characterize a diffused seismicity under the common assumption that this background seismic rate is invariant over time.

@@

%------------------------------------------------------------------------------

\subsubsection{Local bandwidth computation}
%------------------------------------------------------------------------------

@@

The bandwidths are defined locally. Could be small in high earthquake density regions and higher where earthquakes are rarely or regions with information lack.

%------------------------------------------------------------------------------

\subsubsection{Stationary seismic rate}
%------------------------------------------------------------------------------

After compute the model parameters and completely define it, the time-independent or stationary seismic rate $\bar{R}$ on each location $\boldsymbol{r}_0$ have to be computed.
The way to do it proposed by \citet{helmstetter_2012} was to get the median
on $\boldsymbol{r}_0$ over all considered time window:
\begin{equation}
	\ensuremath{
		\bar{R}(\boldsymbol{r}_0) = \text{Median}\left[R(\boldsymbol{r}_0, t)\right].
	}
	\label{eq:stationary_rate}
\end{equation}

@@

%------------------------------------------------------------------------------

\subsubsection{Maximum likelihood optimization}
%------------------------------------------------------------------------------

@@

If the earthquake occurrence could be modeled by a Poisson process with rate $N_p$, then the probability to observe exactly $n$ events on the consider time frame is
\begin{equation}
	\ensuremath{
		\gls{sym:pNn} = \frac{{N_p}^n e^{-N_p}}{n!}.
	}
	\label{eq:poisson_probability}
\end{equation}

@@

%----------------------------------------------------------------------------------------
%	R E S U L T S 
%----------------------------------------------------------------------------------------

@@

@@

%----------------------------------------------------------------------------------------
%	D I S C U S S I O N
%----------------------------------------------------------------------------------------

@@

Conclusion comments

@@

% \appendix

% \section{If I'll append something}

% something appended

@@

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.20\textwidth}
% 						 p{0.40\textwidth}
% 						 p{0.40\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_depth}  &
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_weekday} &
% 		\includegraphics[height=5cm]{z_img_hmtk_bsb2014_11_hour}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Catalogue overview. The histogram (a) shows the depth distribution. The histograms (b) and (c) represent the distributions of weekday and hour which earthquakes occur respectively. Dashed lines represent the mean value.}
% 	\label{fig_overview}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\begin{tabular}{ c c }
% 		\footnotesize(a)
% 		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_rate}
% 		\\
% 		\footnotesize(b)
% 		& \includegraphics[width=0.40\textwidth]{z_img_time_mag_count_br_1960}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Earthquakes by year (a) and discriminated by magnitude (b).}
% 	\label{fig_records}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		%\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\begin{tabular}{ c c }
% 		\footnotesize(a)
% 		& \includegraphics[width=0.45\textwidth]{z_img_hmtk_bsb2014_11_decluster}
% 		\\
% 		\footnotesize(b)
%         & \includegraphics[width=0.40\textwidth]{z_img_hmtk_bsb2014_11_clusters}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Decluster evaluation (a) and the clusters map (b).}
% 	\label{fig_decluster}
% 	\end{center}
% \end{figure}

% \begin{figure}
%     \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_completeness}
%     \caption{Completeness}
%     \label{fig_completeness}
% \end{figure}

% \begin{figure}
%     \includegraphics[width=.45\linewidth]{z_img_hmtk_bsb2014_11_recurrence}
%     \caption{Annual earthquake recurrence.}
%     \label{fig_occurrence}
% \end{figure}

% % =========
% % Methods
% % =========

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_woo_bandwidth}
% 	\caption{Magnitude dependence bandwidth.}
% 	\label{fig_woo_bandwidth}
% \end{figure}

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_hidi}
% 	\caption{Local bandwidth example.}
% 	\label{fig_helmstetter_hidi}
% \end{figure}

% % % TODO add HI_DI histograms

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_stationary_a}
% 	\caption{Stationary seismic rate}
% 	\label{fig_helmstetter_stationary_rate}
% \end{figure}

% \begin{figure}
% 	\includegraphics[width=0.4\linewidth]{z_img_helmstetter_catalogues}
% 	\caption{Learning and target catalogs.}
% 	\label{fig_helmstetter_catalogues}
% \end{figure}

% % =========
% % Smoothed Rates
% % =========

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.33\textwidth}
% 						 p{0.34\textwidth}
% 						 p{0.33\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_a_frankel_br}  &
% 		\includegraphics[height=5cm]{z_img_a_woo} &
% 		\includegraphics[height=5cm]{z_img_a_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Smoothed rates comparison: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectively.}
% 	\label{fig_rates}
% 	\end{center}
% \end{figure}

% % =========
% % Results
% % =========

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.33\textwidth}
% 						 p{0.34\textwidth}
% 						 p{0.33\textwidth} }
% 		\footnotesize(a) &
% 		\footnotesize(b) &
% 		\footnotesize(c)
% 		\\
% 		\includegraphics[height=5cm]{z_img_pga_frankel}  &
% 		\includegraphics[height=5cm]{z_img_pga_woo} &
% 		\includegraphics[height=5cm]{z_img_pga_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{PGA (poe 10\%/50y) comparison for (a) \citet{frankel_1995}, (b) \citet{woo_1996} and (c) \citet{helmstetter_2012} methods.}
% 	\label{fig_pga}
% 	\end{center}
% \end{figure}

% \begin{figure}
% 	\begin{center}
% 	\begin{table}[H]
% 		\begin{tabular}{ p{0.5\textwidth} p{0.5\textwidth} }
% 		\footnotesize(a)
% 		&
% 		\footnotesize(b)
% 		\\
% 		\includegraphics[width=0.45\textwidth]{z_img_pga_gshap} &
% 		\includegraphics[width=0.45\textwidth]{z_img_pga_helmstetter}
% 		\end{tabular}
% 	\end{table}
% 	\caption{Previous available Brazilian PSHA from (a) GSHAP project and the PSHA proposed by this work (b). }
% 	\label{placeholder}
% 	\end{center}
% \end{figure}
